---
title: "588 Project"
subtitle: "Cameron Bale"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Install and load packages. Increase memory limit.
```{r}
#install.packages('tidyverse')
#install.packages('quantreg')
library(tidyverse)
library(quantreg)
memory.limit(size = 50000)
```

Create a loop that:

* reads in the data for a given year (2010 - 2013)
* combines the movement data with the store file for the year
* filters for grocery stores in Utah
* joins with the upc file
* saves the full data file
```{r}
products <- read_tsv('products.tsv', quote = "")

years <- c(10, 11, 12, 13)

for (i in seq_along(years)) {

  move <- read_tsv(paste0('1344_20', years[i], '.tsv'))
  stores <- read_tsv(paste0('stores_20', years[i], '.tsv'), guess_max = 200000)

  full <- move %>%
    inner_join(stores, by = 'store_code_uc') %>%
    filter(channel_code == 'F' & fips_state_descr == 'UT') %>%
    inner_join(products, by = 'upc')

  save(full, file = paste0('full_', years[i], '.RData'))

  rm(move, stores, full)

}
```

Load data for all four years and combine.
```{r}
full_data <- tibble()

for (i in seq_along(years)) {
  
  load(paste0('full_', years[i], '.RData'))
  
  full_data <- full_data %>%
    bind_rows(full)
  
}

rm(full)

save(full_data, file = 'full_data.RData')
```

Create sales variable.
```{r}
full_data <- full_data %>%
  filter(price < 12) %>%
  mutate(sales = units * price)
```

Calculate total sales for each price level of each upc. Calculate a dataframe with the log versions of price and 
sales.
```{r}
upc_sales <- full_data %>%
  group_by(upc, price) %>%
  summarize(sales = sum(sales)) %>%
  mutate(units = sales / price)

log_upc_sales <- upc_sales %>%
  mutate(price = log(price), sales = log(sales), units = log(units))
```

Plot sales at each price level for each upc and include the regular OLS line.
```{r}
qs <- 1:9/10

log_upc_sales %>%
  ggplot(aes(x = price, y = sales)) +
  geom_point() +
  geom_smooth(method = 'lm', col = 'red', se = FALSE) +
  geom_quantile(quantiles = qs)
```

Plot price against units sold. (demand curve for cereal category)
```{r}
log_upc_sales %>%
  ggplot(aes(x = units, y = price)) +
  geom_point() +
  geom_smooth(method = 'lm', color = 'red') +
  geom_quantile(quantiles = qs)
```

Run simple OLS regression of sales on price.
```{r}
log_upc_sales %>%
  lm(sales ~ price, data = .) %>%
  summary()
```

Run simple OLS regression of price on units.
```{r}
log_upc_sales %>%
  lm(price ~ units, data = .) %>%
  summary()
```

Quantile regression for sales on price.
```{r}
qr_sp <- log_upc_sales %>%
  rq(sales ~ price, data = ., tau = qs)
```

Plot significance of quantile coefficient estimates.
```{r}
plot(summary(qr_sp), parm = "price")
```

Regression of price on units.
```{r}
qr_pu <- log_upc_sales %>%
  rq(price ~ units, data = ., tau = qs)
```

Plot significance of quantile coefficient estimates.
```{r}
plot(summary(qr_pu), parm = "units")
```

Add brand description to data.
```{r}
full_brands <- full_data %>%
  select(upc, brand_descr, brand_code_uc) %>%
  distinct() %>%
  arrange(upc)

temp <- log_upc_sales %>%
  left_join(full_brands, by = 'upc')
```

Create a vector 'mult_brands' for upcs that have multiple brand descriptions.
```{r}
upcs <- unique(full_brands$upc)
mult_brands <- c()

for (i in seq_along(upcs)) {
  
  brand_test <- full_brands %>%
    filter(upc == upcs[i])

  if (nrow(brand_test) > 1) {
  
    mult_brands <- c(mult_brands, upcs[i])
  
  }
}
```

Remove brands with multiple descriptions from data.
```{r}
full_brands <- full_brands %>%
  filter(!upc %in% mult_brands)

log_upc_sales <- log_upc_sales %>%
  filter(!upc %in% mult_brands)
```

Join brand descriptions to log upc sales.
```{r}
temp <- log_upc_sales %>%
  left_join(full_brands, by = 'upc')
```

































