---
title: "588 Project"
subtitle: "Cameron Bale"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Install and load packages. Increase memory limit.
```{r}
#install.packages('tidyverse')
#install.packages('quantreg')
library(tidyverse)
library(quantreg)
memory.limit(size = 50000)
```

Create a loop that:

* reads in the data for a given year (2010 - 2013)
* combines the movement data with the store file for the year
* filters for grocery stores in Utah
* joins with the upc file
* saves the full data file
```{r}
products <- read_tsv('products.tsv', quote = "")

years <- c(10, 11, 12, 13)

for (i in seq_along(years)) {

  move <- read_tsv(paste0('1344_20', years[i], '.tsv'))
  stores <- read_tsv(paste0('stores_20', years[i], '.tsv'), guess_max = 200000)

  full <- move %>%
    inner_join(stores, by = 'store_code_uc') %>%
    filter(channel_code == 'F' & fips_state_descr == 'UT') %>%
    inner_join(products, by = 'upc')

  save(full, file = paste0('full_', years[i], '.RData'))

  rm(move, stores, full)

}
```

Load data for all four years and combine.
```{r}
full_data <- tibble()

for (i in seq_along(years)) {
  
  load(paste0('full_', years[i], '.RData'))
  
  full_data <- full_data %>%
    bind_rows(full)
  
}

rm(full)

save(full_data, file = 'full_data.RData')
```

Create sales variable.
```{r}
full_data <- full_data %>%
  mutate(sales = units * price)
```

Calculate total sales for each price level of each upc. Calculate a dataframe with the log versions of price and sales.
```{r}
upc_sales <- full_data %>%
  group_by(upc, price) %>%
  summarize(sales = sum(sales))

log_upc_sales <- upc_sales %>%
  mutate(price = log(price), sales = log(sales))
```

Plot sales at each price level for each upc.
```{r}
log_upc_sales %>%
  ggplot(aes(x = price, y = sales)) +
  geom_point()
```













